Binocular integration of chromatic and luminance signals

### 2024-04-16 manuscript.qmd
Fixed python again
Added axis breaks!

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
    ticklocsy <- seq(-24,30,6)
    ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)

@@

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)

@@

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(-6,18))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)

@@

  ticklocsx <- seq(-24,30,6)
  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
  ticklocsy <- seq(-24,30,6)
  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(a) Flickering disc (thresholds)',cex.main=1.5)

@@

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-6,18))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(b) Flickering disc (slopes)',cex.main=1.5)

@@

  ticklocsx <- seq(-24,30,6)
  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
  ticklocsy <- seq(-24,30,6)
  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=2.4, cex.lab=1.5)
  title(main=paneltitles[expt],cex.main=2)
  # pedcontrasts <- seq(-12,30,6)

@@

  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(0,100))  
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
  title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
  title(main=titlelist[cond],cex.main=2)

@@

axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized target contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
  title(main=titlelist[cond+3],cex.main=2)

@@

ticklocsx <- seq(-24,30,6)
ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
ticklocsy <- seq(-24,30,6)
ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)

@@

ticklocsx <- seq(-24,30,6)
ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
ticklocsy <- seq(-24,30,6)
ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
pnos <- c(1,6,7)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)

>>>>

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','reticulate','osfr','bookdown','rstan','coda','modeest','pals','pracma','parallel','doParallel','R.matlab','bayestestR','alphahull','kableExtra','plotrix') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
    ticklocsy <- seq(-24,30,6)
    ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)
    axis.break(axis=1,breakpos=-18)

@@

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)

@@

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(-6,18))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)
    axis.break(axis=1,breakpos=-18)

@@

  ticklocsx <- seq(-24,30,6)
  ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
  ticklocsy <- seq(-24,30,6)
  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(a) Flickering disc (thresholds)',cex.main=1.5)
  axis.break(axis=1,breakpos=-18)

@@

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-6,18))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(b) Flickering disc (slopes)',cex.main=1.5)
  axis.break(axis=1,breakpos=-18)

@@

  ticklocsx <- seq(-24,30,6)
  ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
  ticklocsy <- seq(-24,30,6)
  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=2.4, cex.lab=1.5)
  title(main=paneltitles[expt],cex.main=2)
  axis.break(axis=1,breakpos=-18)

@@

  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(0,100))  
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized target contrast", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
  title(ylab="Percent correct", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
  title(main=titlelist[cond],cex.main=2)

@@

axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized target contrast", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)    # titles for axes
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
  title(main=titlelist[cond+3],cex.main=2)

@@

ticklocsx <- seq(-24,30,6)
ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
ticklocsy <- seq(-24,30,6)
ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+1)],')  P',p,': Achromatic'),cex.main=2)
axis.break(axis=1,breakpos=-18)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+2)],')  P',p,': Red/Green'),cex.main=2)
axis.break(axis=1,breakpos=-18)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[(3*(p-1)+3)],')  P',p,': Blue/Yellow'),cex.main=2)
axis.break(axis=1,breakpos=-18)

@@

ticklocsx <- seq(-24,30,6)
ticklabelsx <- c(0,' ','1/4','1/2',1,2,4,8,16,32)
ticklocsy <- seq(-24,30,6)
ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)
pnos <- c(1,6,7)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Normalized pedestal contrast", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Normalized threshold", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
title(main=paste0('(',letters[p],')  P', pnos[p] ,': Flickering disc'),cex.main=2)
axis.break(axis=1,breakpos=-18)
